---
title: "Cybersecurity and Future of Working from Home"
author: "LetingZhang"
date: "11/22/2020"
output: html_document
---

# Preperation

```{r Load packages, include=FALSE }
library(dplyr, warn.conflicts = FALSE)
library(tidyverse)
library(ggplot2)
library(urbnmapr)
library(plm)
library(DT)
library(R.utils)
library(data.table)
library(reshape)
library(data.table)
library(tidycensus)
devtools::install_github("kjhealy/socviz")
```

```{r R Markdown setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data loading


## Cybersecurity investment data from CI database----
```{r CI data, include=FALSE}

ci_path <- readWindowsShortcut("data/CI_USA_2019.lnk")

ci_path <- gsub("\\\\", "/", ci_path$pathname)

ci_cyber <- read.csv("data/CI_cyber_use.csv")

ci_cyber <- subset(ci_cyber, select = c('SITEID','cyber_sum', 'IT_STAFF','PCS'))

path <- paste(ci_path, '/SiteDescription.TXT', sep = '')

col <-  c('SITEID', 'PRIMARY_DUNS_NUMBER', 'COMPANY', 'CITY','STATE','ZIPCODE','COUNTRY' ,'YEAR_EST', 'COUNTY_NAME',    'MSA','EMPLE','REVEN','SALESFORCE','MOBILE_WORKERS','MOBILE_INTL', 'IT_STAFF', 'PC_BUDGET', 'SICGRP', 'SICSUBGROUP')
ci_site <- fread(path, select = col)

path <- paste(ci_path, '/PresenceInstall.TXT', sep = '')

col <-  c('SITEID', 'VPN_PRES', 'IDACCESS_SW_PRES', 'DBMS_PRES', 'DATAWAREHOUSE_SW_PRES', 'SECURITY_SW_PRES')

ci_presence <- fread(path, select = col)
ci_presence[ci_presence == "Yes"] <- 1
ci_presence[ci_presence == ""] <- 0
ci_presence <- as.data.frame(ci_presence)
ci_presence[, 2:6] <- sapply(ci_presence[, 2:6], as.numeric )

path <- paste(ci_path, '/ITSpend.TXT', sep = '')
ci_itspend <- fread(path)
ci_itspend<- as.data.frame(ci_itspend)

path <- paste(ci_path, '/SiteLevelEnterprise.TXT', sep = '')
col <-  c('SITEID', 'ENT_ID', 'ENT_COMPANY', 'CORPHDQ', 'ENT_TYPE', 'ENT_EMPLE', 'ENT_REVEN', 'ENT_IT_EMPLE','ENT_SERVER','ENT_STORAGE' , 'ENT_INTERNET_USERS', 'ENT_SERVER_BUDGET', 'ENT_TERMINAL_BUDGET', 'ENT_STORAGE_BUDGET','ENT_COMM_BUDGET', 'ENT_SERVICES_BUDGET')
ci_enterprise <-  fread(path, select = col)


```

```{r load cencus data & geography crosswalk file, include=FALSE}
#source: census website PS: USE THE NEW ONE 
#industry_code <- read.csv("cps_monthly_data/2017-census-industry-classification-titles-and-code-list.csv")
#occupation_code<-read.csv("cps_monthly_data/2018-census-occupation-classification-titles-and-code-list.csv")
geo_code <- read.csv("data/geocorr2018 -crosswalk.csv")

#source: https://www.huduser.gov/portal/datasets/usps_crosswalk.html
zip_county <- read.csv("data/ZIP_COUNTY_122019.csv")

#source: https://data.nber.org/cbsa-msa-fips-ssa-county-crosswalk/2019/
msa_county <- read.csv("data/COUNTY_METRO2019.CSV")

# EconomicTrack
geoid <- read.csv("data/GeoIDs - County.csv", stringsAsFactors = F)

```

## EconomicTracker data

```{r load EconomicTracker data }

#source: https://github.com/OpportunityInsights/EconomicTracker

## Main DV
ui_state <- read.csv("data/EconomicTracker-main/data/UI Claims - State - Weekly.csv", stringsAsFactors = F)
ui_county <- read.csv("data/EconomicTracker-main/data/UI Claims - County - Weekly.csv", stringsAsFactors = F)
ui_county$initclaims_count_regular<- as.numeric(ui_county$initclaims_count_regular)
ui_county$initclaims_rate_regular <- as.numeric(ui_county$initclaims_rate_regular)

ui_state <- ui_state%>% mutate_if(is.character,as.numeric)


employment_county <- read.csv("data/EconomicTracker-main/data/Employment Combined - County - Daily.csv")
employment_city <- read.csv("data/EconomicTracker-main/data/Employment Combined - City - Daily.csv")
employment_state <- read.csv("data/EconomicTracker-main/data/Employment Combined - State - Daily.csv")


employment_county[, c(5:8)] <- apply(employment_county[, c(5:8)], 2, function(x) as.numeric(x))
employment_county <- employment_county%>% mutate_if(is.character,as.numeric)
employment_state <- employment_state%>% mutate_if(is.character,as.numeric)

employ_data_ori <- employ_data
employ_data <- employment_county
employ_data[, c(5:8)] <- apply(employ_data[, c(5:8)], 2, function(x) as.numeric(x))


## Other
affinity_city <- read.csv("data/EconomicTracker-main/data/Affinity - City - Daily.csv")
affinity_county <- read.csv("data/EconomicTracker-main/data/Affinity - County - Daily.csv")
affinity_state <- read.csv("data/EconomicTracker-main/data/Affinity - State - Daily.csv")
  
jobpost_city_week <- read.csv("data/EconomicTracker-main/data/Burning Glass - City - Weekly.csv")
jobpost_state_week <- read.csv("data/EconomicTracker-main/data/Burning Glass - state - Weekly.csv")

gogmobility_city <- read.csv("data/EconomicTracker-main/data/Google Mobility - City - Daily.csv")
gogmobility_county <- read.csv("data/EconomicTracker-main/data/Google Mobility - County - Daily.csv")
gogmobility_state <- read.csv("data/EconomicTracker-main/data/Google Mobility - State - Daily.csv")

smallbus_city <- read.csv("data/EconomicTracker-main/data/Womply Merchants - City - Daily.csv")
smallbus_county <- read.csv("data/EconomicTracker-main/data/Womply Merchants - County - Daily.csv")
smallbus_state <- read.csv("data/EconomicTracker-main/data/Womply Merchants - State - Daily.csv")

smallrev_city <- read.csv("data/EconomicTracker-main/data/Womply Revenue - City - Daily.csv")
smallrev_county <- read.csv("data/EconomicTracker-main/data/Womply Revenue - County - Daily.csv")
smallrev_state <- read.csv("data/EconomicTracker-main/data/Womply Revenue - State - Daily.csv")

econ_county <- Reduce(function(x, y) merge(x, y, all=TRUE), list(affinity_county,  gogmobility_county,   
                                                                smallbus_county,smallrev_county ))
econ_county[, c(8:14)] <- apply(econ_county[, c(8:14)], 2, function(x) as.numeric(x))

econ_state <- Reduce(function(x, y) merge(x, y, all=TRUE), list(affinity_state,jobpost_state_week,
                                                                gogmobility_state, smallbus_state ,smallrev_state ))
econ_state <- econ_state[, -c(5)]
econ_state <- econ_state%>% mutate_if(is.character,as.numeric)

covid_county <- covid_county%>% mutate_if(is.character,as.numeric)



```


## State stay-at-home order data
```{r load state policy data and clean (ealier) Shelter-in-plance data, include=FALSE}
# source: EconomicTracker 

state_policy  <- read.csv("data/Policy Milestones - State.csv", stringsAsFactors = F)
colnames(state_policy)[1] <- "state"
#Source: https://www.finra.org/rules-guidance/key-topics/covid-19/shelter-in-place
#Reference: https://www.nytimes.com/interactive/2020/us/coronavirus-stay-at-home-order.html
shelterdate <- read.csv("data/shelter-in-place.csv")
shelterdate$State <- str_replace_all(shelterdate$State, "[*]", "") #Remove * in state names


state_info<-data.frame(abb = state.abb, state = state.name)
state_info[] <- lapply(state_info, as.character)

state_info[nrow(state_info) + 1,] = c( "DC", "District of Columbia")
state_info[nrow(state_info) + 1,] = c("PR", "Puerto Rico")


shelterdate <- merge(shelterdate,state_info, by.x = "State", by.y = "state", all.x = TRUE )
shelterdate$Order.Date <- str_replace_all(shelterdate$Order.Date, "/2020", "") #Remove * in state names
shelterdate$Order.Date1 <- shelterdate$Order.Date

shelterdate <- shelterdate %>% separate("Order.Date1", c("OrderMonth", "OrderDay"))

shelterdate$OrderMonth <- as.integer(shelterdate$OrderMonth)
shelterdate$OrderDay <- as.integer(shelterdate$OrderDay)

#National Emergency Concerning: March 13 
#Reference: https://www.whitehouse.gov/presidential-actions/proclamation-declaring-national-emergency-concerning-novel-coronavirus-disease-covid-19-outbreak/
```


## Covid19-data 

```{r load covid19-data, include=FALSE}

covid_county <- read.csv("data/EconomicTracker-main/data/COVID - County - Daily.csv", stringsAsFactors = F)
covid_state <- read.csv("data/EconomicTracker-main/data/COVID - State - Daily.csv", stringsAsFactors = F)
covid_county <- covid_county%>% mutate_if(is.character,as.numeric)
covid_state<- covid_state%>% mutate_if(is.character,as.numeric)

```

## Unemployement data from IPUMS CPS
```{r load unemployement data ipums CPS,include=FALSE}
#source: ipums
library(ipumsr)
# Change these filepaths to the filepaths of your downloaded extract
cps_ddi_file <- "data/cps_00003.xml"
cps_data_file <- "data/cps_00003.dat"
cps_ddi <- read_ipums_ddi(cps_ddi_file) # Contains metadata, nice to have as separate object
cps_data <- read_ipums_micro(cps_ddi_file, data_file = cps_data_file)
fread(file_path, select = col)
```


# Data transformation & Descriptive analysis 
```{r CI merge, include=FALSE}
#Geo merge
ci_data_key <- ci_site[, c("SITEID","ZIPCODE")]
ci_data_key$ZIPCODE <- substr(ci_site[, c("SITEID","ZIPCODE")]$ZIPCODE,1,5)
ci_data_key$ZIPCODE <- sub("^0+", "", ci_data_key$ZIPCODE)
ci_data_key$ZIPCODE <- as.integer(ci_data_key$ZIPCODE)

ci_data_key <- merge(ci_data_key, zip_county_use[, c("ZIP", "COUNTY")], by.x = "ZIPCODE", by.y = "ZIP", all.x = TRUE)
ci_data_key <- merge(ci_data_key, msa_county_use, by.x = "COUNTY", by.y = "FIPS.County.Code",all.x = TRUE )
#Merge
ci_data_use <- merge(ci_site, ci_data_key[, -2], by = "SITEID",all.x = TRUE)
ci_data_use <- merge(ci_data_use, ci_cyber, by = "SITEID",all.x = TRUE)
ci_data_use <- merge(ci_data_use, ci_presence, by = "SITEID",all.x = TRUE)
ci_data_use <- merge(ci_data_use, ci_itspend, by = "SITEID",all.x = TRUE)
ci_data_use <- merge(ci_data_use, ci_enterprise, by = "SITEID",all.x = TRUE)

```

```{r Aggregate data at county level, include=FALSE}
# Unemployement insurance: county, week -> county, month
ui_mean_county <- ui_county %>% 
  group_by(month, countyfips) %>% 
  summarise (avg_initclaims_count = mean(initclaims_count_regular, na.rm = T),
             avg_initclaims_rate = mean(initclaims_rate_regular, na.rm = T)  )

# Employment rate: county, day -> county, month
employ_mean_county <- employment_county %>% 
  group_by(month, countyfips) %>% 
  summarise_at(c("emp_combined","emp_combined_inclow", "emp_combined_incmiddle", "emp_combined_inchigh"), mean, na.rm = TRUE)

# CI: site -> county (sum)

ci_sum_county<- ci_data_use %>% select(SITEID, STATE, COUNTY,CBSA.Name, EMPLE, REVEN, MOBILE_WORKERS 
                                       ,cyber_sum,VPN_PRES,IDACCESS_SW_PRES,
                                       DBMS_PRES, DATAWAREHOUSE_SW_PRES, SECURITY_SW_PRES, PCS, IT_BUDGET, HARDWARE_BUDGET, 
                                       SOFTWARE_BUDGET,SERVICES_BUDGET) %>% 
            group_by(COUNTY) %>% 
           summarise_at(c('EMPLE', 'REVEN', 'MOBILE_WORKERS','cyber_sum','VPN_PRES','IDACCESS_SW_PRES', 'DBMS_PRES', 'DATAWAREHOUSE_SW_PRES', 'SECURITY_SW_PRES', 'PCS', 'IT_BUDGET', 'HARDWARE_BUDGET', 'SOFTWARE_BUDGET','SERVICES_BUDGET'), sum, na.rm = TRUE)


# 
#    summarise(number_sites = n(), 
#          employee = sum(EMPLE),
#          revenue = sum(REVEN),
#          cyber = sum(cyber_sum, na.rm=T),
#          pc = sum(PCS,  na.rm=T),
#          vpn_pres = sum(vpn_pres, na.rm = T),
#          idaccess_pres = sum()
#          it_budget = sum(IT_BUDGET,  na.rm=T),
#          hard_budget = sum(HARDWARE_BUDGET,  na.rm=T),
#          soft_budget = sum(SOFTWARE_BUDGET, na.rm=T),
#          service_budget = sum(SERVICES_BUDGET, na.rm=T)
#          )
#          

# Econ: county, day -> county, month

econ_mean_county <- econ_county %>% 
  group_by(month, countyfips) %>% 
  summarise_at(c('spend_all','gps_retail_and_recreation','gps_grocery_and_pharmacy','gps_parks', 'gps_transit_stations',
                 'gps_workplaces', 'gps_residential', 'gps_away_from_home', 'merchants_all', 'revenue_all'), mean, na.rm = TRUE)

# Covid: county, day -> county,month

covid_stat_county <-  covid_county %>% 
  group_by(countyfips,month) %>% 
  summarise(case_count = max(case_count, na.rm = T),
            death_count = max(death_count, na.rm = T),
            case_rate = max(case_rate, na.rm = T),
            death_rate = max(death_rate, na.rm = T),
            avg_new_case_count = mean(new_case_count, na.rm = T),
            avg_new_death_rate = mean(new_death_count, nna.rm = T),
            avg_new_case_rate = mean(new_case_count, na.rm = T),
            avg_new_death_rate = mean(new_death_count, na.rm =T),
             
             )


# Aggregation

data_county <- ui_mean_county %>% 
  full_join(employ_mean_county, c('month', 'countyfips') ) %>% 
  full_join(geoid[, c('countyfips', 'statefips', 'stateabbrev')], 'countyfips' ) %>% 
  full_join(econ_mean_county, c('month', 'countyfips')) %>% 
  full_join(covid_stat_county, c('month', 'countyfips')) %>% 
  full_join(state_policy, c('statefips')) %>% 
  full_join(shelterdate[, c('abb', 'OrderMonth', 'OrderDay')], c('stateabbrev' = 'abb') )



```
```{r Aggregate data at state level, include=FALSE}


# Unemployement insurance: state, week -> state, month
ui_mean_state <- ui_state %>% 
  group_by(month,statefips) %>% 
  summarise_at(c('initclaims_count_regular', 'initclaims_rate_regular', 'contclaims_count_regular', 'contclaims_rate_regular', 'initclaims_count_pua', 'contclaims_count_pua'), mean, na.rm = TRUE)

# Employment rate: county, day -> county, month
employ_mean_state <- employment_state %>% 
  group_by(month, statefips) %>% 
  summarise_at(c("emp_combined","emp_combined_inclow", "emp_combined_incmiddle", "emp_combined_inchigh",  "emp_combined_ss40", "emp_combined_ss60", "emp_combined_ss65", "emp_combined_ss70" ), mean, na.rm = TRUE)
  


# CI: site -> state (sum)

ci_sum_state<- ci_data_use %>% select(SITEID, STATE, COUNTY,CBSA.Name, EMPLE, REVEN, MOBILE_WORKERS ,cyber_sum,VPN_PRES,IDACCESS_SW_PRES, DBMS_PRES, DATAWAREHOUSE_SW_PRES, SECURITY_SW_PRES, PCS, IT_BUDGET, HARDWARE_BUDGET, SOFTWARE_BUDGET,SERVICES_BUDGET) %>% 
  group_by(STATE) %>% 
  summarise_at(c('EMPLE', 'REVEN', 'MOBILE_WORKERS','cyber_sum','VPN_PRES','IDACCESS_SW_PRES', 'DBMS_PRES', 'DATAWAREHOUSE_SW_PRES', 'SECURITY_SW_PRES', 'PCS', 'IT_BUDGET', 'HARDWARE_BUDGET', 'SOFTWARE_BUDGET','SERVICES_BUDGET'), sum, na.rm = TRUE)


# ci_sum_state <- ci_data_use %>% select(SITEID, STATE, COUNTY,CBSA.Name, EMPLE, REVEN, MOBILE_WORKERS ,cyber_sum,VPN_PRES,IDACCESS_SW_PRES, DBMS_PRES, DATAWAREHOUSE_SW_PRES, SECURITY_SW_PRES, PCS, IT_BUDGET, HARDWARE_BUDGET, SOFTWARE_BUDGET,SERVICES_BUDGET) %>%
#   group_by(STATE) %>%
#    summarise(number_sites = n(),
#          employee = sum(EMPLE),
#          revenue = sum(REVEN),
#          cyber = sum(cyber_sum, na.rm=T),
#          pc = sum(PCS,  na.rm=T),
#          it_budget = sum(IT_BUDGET,  na.rm=T),
#          hard_budget = sum(HARDWARE_BUDGET,  na.rm=T),
#          soft_budget = sum(SOFTWARE_BUDGET, na.rm=T),
#          service_budget = sum(SERVICES_BUDGET, na.rm=T),
#          )

# Econ: state, day -> state, month
econ_mean_state <- econ_state%>% 
  group_by(month, statefips) %>% 
  summarise_at(vars(spend_acf:revenue_ss70), mean, na.rm = TRUE)


# Covid: state, day -> state,month

covid_stat_state <-  covid_state %>% 
  group_by(month, statefips) %>% 
  summarise(test_count = max(test_count, na.rm = T),
            test_rate = max(test_rate, na.rm = T),
            case_count = max(case_count, na.rm = T),
            death_count = max(death_count, na.rm = T),
            case_rate = max(case_rate, na.rm = T),
            death_rate = max(death_rate, na.rm = T),
            avg_new_case_count = mean(new_case_count, na.rm = T),
            avg_new_death_rate = mean(new_death_count, nna.rm = T),
            avg_new_case_rate = mean(new_case_count, na.rm = T),
            avg_new_death_rate = mean(new_death_count, na.rm =T),
             
             )


# Aggregation

data_state <- ui_mean_state %>% 
  full_join(employ_mean_state, c('month', 'statefips') ) %>% 
 left_join(geoid[, c('statefips', 'stateabbrev')], 'statefips' ) %>% 
  unique() %>% 
  full_join(econ_mean_state, c('month', 'statefips')) %>% 
  full_join(covid_stat_state, c('month', 'statefips')) %>% 
  full_join(state_policy, c('statefips')) %>% 
  full_join(shelterdate[, c('abb', 'OrderMonth', 'OrderDay')], c('stateabbrev' = 'abb') )


demo <- ui_mean_state %>% 
  full_join(employ_mean_state, c('month', 'statefips') ) %>% 
 left_join(geoid[, c('statefips', 'stateabbrev')], 'statefips' ) %>% 
  unique() %>% 
  full_join(ci_sum_state, c('stateabbrev'='STATE')) %>% 
  full_join(econ_mean_state, c('month', 'statefips')) %>% 
  full_join(covid_stat_state, c('month', 'statefips')) %>% 
  full_join(state_policy, c('statefips')) %>% 
  full_join(shelterdate[, c('abb', 'OrderMonth', 'OrderDay')], c('stateabbrev' = 'abb') )


rm(demo1)
```

```{r Summary data at county and state level}
summary(data_county)
summary(data_state)

write.csv(data_county, "data/output/data_county.csv")
write.csv(data_state, "data/output/data_state.csv")
```

## Descriptive analysis

```{r}
# State level

long_data_state <- melt(data_state, id=c("month", "newmonth", "statefips", "state", "stateabbrev") ) # convert to long format

###Employment in industries
long_data_state %>% filter(stateabbrev %in%  c("PA", "NY", "CA", "ND", "IA", "NE") &
                             variable %in% c("emp_combined_ss40", "emp_combined_ss60",
                                          "emp_combined_ss65", "emp_combined_ss70")) %>% 
                mutate_at("value", as.numeric) %>% 
                ggplot(aes(newmonth, value, colour=variable, group = variable)) +
    geom_line() + 
   facet_wrap(~stateabbrev, nrow =2)+
    theme_bw()


  
```
```{r}
### Affinty /Expenditure ###
long_data_state %>% filter(stateabbrev %in% c("PA", "NY", "CA", "ND", "IA", "NE") &
                             variable %in% c("spend_all_inchigh", "spend_all_incmiddle", "spend_all_inclow", "spend_all_q2", "spend_all_q3")) %>% 
                mutate_at("value", as.numeric) %>% 
                ggplot(aes(newmonth, value, colour=variable, group = variable)) +
    geom_line() + 
  facet_wrap(~stateabbrev, nrow =2)+
    theme_bw()

```



```{r}

long_data_state %>% filter(stateabbrev %in% c("PA", "NY", "CA", "ND", "IA", "NE") &
                             variable %in% c("spend_acf", "spend_aer", "spend_all", "spend_apg", "spend_grf", "spend_hcs", "spend_tws")) %>% 
                mutate_at("value", as.numeric) %>% 
                ggplot(aes(newmonth, value, colour=variable, group = variable)) +
    geom_line() + 
  facet_wrap(~stateabbrev, nrow =2)+
    theme_bw()


```

```{r}
### Merchants ###
long_data_state %>% filter(stateabbrev %in% c("PA", "NY", "CA", "ND", "IA", "NE") &
                             variable %in% c("merchants_all", "merchants_inchigh", "revenue_incmiddle", "revenue_inclow")) %>% 
                mutate_at("value", as.numeric) %>% 
                ggplot(aes(newmonth, value, colour=variable, group = variable)) +
    geom_line() + 
  facet_wrap(~stateabbrev, nrow =2)+
    theme_bw()


```
```{r}
long_data_state %>% filter(stateabbrev %in% c("PA", "NY", "CA", "ND", "IA", "NE") &
                             variable %in% c("merchants_ss40", "merchants_ss60", "revenue_ss65", "revenue_ss70")) %>% 
                mutate_at("value", as.numeric) %>% 
                ggplot(aes(newmonth, value, colour=variable, group = variable)) +
    geom_line() + 
  facet_wrap(~stateabbrev, nrow =2)+
    theme_bw()

```

```{r}

long_data_state %>% filter(stateabbrev %in% c("PA", "NY", "CA", "ND", "IA", "NE") &
                             variable %in% c("revenue_all", "revenue_inchigh", "revenue_inclow", "revenue_incmiddle")) %>% 
                mutate_at("value", as.numeric) %>% 
                ggplot(aes(newmonth, value, colour=variable, group = variable)) +
    geom_line() + 
  facet_wrap(~stateabbrev, nrow =2)+
    theme_bw()

```
```{r}

long_data_state %>% filter(stateabbrev %in% c("PA", "NY", "CA", "ND", "IA", "NE") &
                             variable %in% c("revenue_ss40", "revenue_ss60", "revenue_ss65", "revenue_ss70")) %>% 
                mutate_at("value", as.numeric) %>% 
                ggplot(aes(newmonth, value, colour=variable, group = variable)) +
    geom_line() + 
  facet_wrap(~stateabbrev, nrow =2)+
    theme_bw()
```

```{r}
# Descriptive analysis


data_state %>% 
  filter(stateabbrev == "PA" ) %>% 
   ggplot(mapping = aes(x = newmonth, group = 1)) +
  geom_line( aes(y =  emp_combined_ss40), size = 1) + 
  geom_line( aes(y =  emp_combined_ss60) , color ="#48CAE4"  , linetype="twodash", size = 1) +
  geom_line( aes(y =  emp_combined_ss65), color = "#0096C7", linetype="twodash", size = 1) +
  geom_line( aes(y =  emp_combined_ss70), color = "#03045E", linetype="twodash", size = 1) +
  ggtitle("Relative changes to employment rates" ) +
  theme(plot.title = element_text(hjust = 0.5))
  

data_state %>% 
  filter(stateabbrev == "PA" ) %>% 
   ggplot(mapping = aes(x = newmonth, group = 1)) +
  geom_line( aes(y =  emp_combined), size = 1) + 
  geom_line( aes(y =  emp_combined_inclow) , color ="#48CAE4"  , linetype="twodash", size = 1) +
  geom_line( aes(y =  emp_combined_incmiddle), color = "#0096C7", linetype="twodash", size = 1) +
  geom_line( aes(y =  emp_combined_inchigh), color = "#03045E", linetype="twodash", size = 1) +
  ggtitle("Relative changes to employment rates (High, Middle, All, Low)" ) +
  theme(plot.title = element_text(hjust = 0.5))
  

```

## Variations 
  
```{r, include=FALSE}


ci_county_mean <- ci_data_use %>% select(SITEID, STATE, ZIPCODE.x, COUNTY,CBSA.Name, EMPLE, REVEN, cyber_sum,PCS, IT_BUDGET, HARDWARE_BUDGET, SOFTWARE_BUDGET,SERVICES_BUDGET) %>% 
  group_by(COUNTY) %>% 
  summarise_at(c("EMPLE","REVEN", "cyber_sum", "PCS", "IT_BUDGET", "HARDWARE_BUDGET", "SOFTWARE_BUDGET" , "SERVICES_BUDGET"), mean, na.rm = TRUE) %>% 
  arrange(desc(SOFTWARE_BUDGET))


ci_county_median <- ci_data_use %>% select(SITEID, STATE, ZIPCODE.x, COUNTY,CBSA.Name, EMPLE, REVEN, cyber_sum,PCS, IT_BUDGET, HARDWARE_BUDGET,SOFTWARE_BUDGET,SERVICES_BUDGET) %>% 
  group_by(COUNTY) %>% 
  summarise_at(c("EMPLE","REVEN", "cyber_sum", "PCS", "IT_BUDGET", "HARDWARE_BUDGET", "SOFTWARE_BUDGET" , "SERVICES_BUDGET"), median, na.rm = TRUE) %>% 
  arrange(desc(cyber_sum))

econ_merge[, 12:18] <- sapply(econ_merge[, 12:18], as.numeric )
```
```{r State level}

state_level %>% 
  group_by(month, stateabbrev) %>% 
  summarise(avg_unemployment = mean(unemployment_rate)) %>% 
  ggplot(aes(y = avg_unemployment,x = YearMonth, group = as.factor(stayathome), colour = as.factor(stayathome))) + 
  geom_line() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title = "Unmployment rate (Average)", x = "Year-Month", y = "Unemployment/Labor force", color = "Stay-at-home-order") +
  scale_color_hue(labels = c("No", "YES")) +
  geom_line(size=2)



```

```{r}

ui_state %>% 
  group_by(month) %>%
  summarise (avg_initclaims_county = sum(month, na.rm = T))

```

```{r Unemployment insurance - Economic Tracker, include=FALSE}

ui_data %>% 
  group_by(month) %>% 
  summarise (avg_initclaims_county = mean(initclaims_count_regular, na.rm = T),
             avg_unemploy_rate = mean(initclaims_rate_regular, na.rm = T)  ) %>% 
  ggplot(mapping = aes(x = as.character(month), y =  avg_unemploy_rate, group = 1)) +
  geom_line() +
  ggtitle("Unmployment insurance claim rates ")+
  theme(plot.title = element_text(hjust = 0.5))
  


employ_data %>% 
  group_by(month) %>% 
  summarise_at(c("emp_combined","emp_combined_inclow", "emp_combined_incmiddle", "emp_combined_inchigh"), mean, na.rm = TRUE) %>% 
  ggplot(mapping = aes(x = as.character(month), group = 1)) +
  geom_line( aes(y =  emp_combined), size = 1) + 
  geom_line( aes(y =  emp_combined_inclow) , color ="#48CAE4"  , linetype="twodash", size = 1) +
  geom_line( aes(y =  emp_combined_incmiddle), color = "#0096C7", linetype="twodash", size = 1) +
  geom_line( aes(y =  emp_combined_inchigh), color = "#03045E", linetype="twodash", size = 1) +
  ggtitle("Relative changes to employment rates (All, Lowincome, Middle income, High income)" ) +
  theme(plot.title = element_text(hjust = 0.5))
  
  

```


o
# Regression Analysis 

```{r create panel data, include=FALSE }


# create mean panel

## Raw data for STATA 

ci_raw <- merge(ci_data_use, geoid[, c("countyfips","statename", "stateabbrev", "county_pop2019")], by.x = "COUNTY", by.y = "countyfips", all.x = TRUE )
write.csv(ci_raw, "data/output/ci_raw.csv")

county_raw <- merge(employ_mean, ui_county_mean , by = c("countyfips","month"), all = T  )
county_raw <- merge(county_raw, geoid[, c("countyfips","statename", "stateabbrev")], by = "countyfips", all.x = TRUE )
county_raw <- merge(county_raw, shelterdate[, c('abb','OrderMonth','OrderDay')], by.x = "stateabbrev", by.y = "abb", all = T)
county_raw <- merge(county_raw, covid_county, by = c('countyfips','month'), all = T)

write.csv(county_raw, "data/output/county_raw.csv")

#econ_mean
write.csv(econ_mean, "data/output/econ_mean.csv")

mean_panel_x <- merge(ci_county_mean, geoid[, c("countyfips","statename", "stateabbrev", "county_pop2019")],
                        by.x = "COUNTY", by.y = "countyfips", all.x = TRUE)
mean_panel_y <- merge(employ_mean, ui_county_mean , by = c("countyfips","month") , all = T  )


mean_panel <- merge(mean_panel_x, mean_panel_y, by.x = "COUNTY", by.y = "countyfips", all = TRUE )

mean_panel <- merge(mean_panel, shelterdate[, c('abb','OrderMonth','OrderDay')], by.x = "stateabbrev", by.y = "abb", all = T)

mean_panel <- mean_panel[c(2,13,1,3:12,14:21)] 


mean_panel <- merge(mean_panel, covid_county, by.x = c('COUNTY','month'), by.y = c('countyfips','month'), all.x = T)

mean_panel <- mean_panel %>% 
  mutate(home = ifelse( (month < OrderMonth) | (is.na(OrderMonth)), 0 ,1),
         mean_cyber = mean(cyber_sum,  na.rm = T),
         mid_cyber = median(cyber_sum, na.rm = T)) 

mean_panel <- mean_panel %>% 
  mutate(high_cyber = ifelse(cyber_sum > mean_cyber, 1, 0))

```

```{r}
# Panel data
pdim(mean_panel)

# Summary statistics 
summary(mean_panel)

```


# Regression Results
```{r Regression}
# fixed effect index

attach(mean_panel)

mean_panel <- mean_panel[order(COUNTY,month),]
panel_use <- mean_panel[which(!is.na(mean_panel$COUNTY) & !is.na(mean_panel$month) ),]
panel_use2 <-mean_panel[,c("COUNTY","month", "avg_initclaims_rate","EMPLE", "REVEN", "PCS")]
write.csv(panel_use, "panel_use.csv")



```

$$ UIClaimRate_it = \beta_{1} StayAtHome_{it}*HighCybersecurity_{i} + \beta_{2} CovidCase_{it}+ \beta_{3} CovidDeath_{it} + county_{i} $$
```{r}

# County fixed effect
reg_fe <- plm(avg_initclaims_rate~home*high_cyber+avg_case_rate+avg_death_rate, data= panel_use)
summary(reg_fe)
```

$$ UIClaimRate_it = \beta_{1} StayAtHome_{it}*HighCybersecurity_{i} + \beta_{2} CovidCase_{it}+  \beta_{3} CovidDeath_{it} + county_{i} + month_{t} $$

```{r}
# Two-way fixed effect
reg_twoway <- plm(avg_initclaims_rate~home*high_cyber+avg_case_rate+avg_death_rate, data= panel_use, model = "within", effect = "twoways")

summary(reg_twoway)

```

$$ UIClaimRate_it = \beta_{1} StayAtHome_{it}*Cybersecurity_{i} + \beta_{2} CovidCase_{it}+  \beta_{3} CovidDeath_{it} + county_{i} + month_{t} $$
```{r}
# Use cybersecurity investment as moderator
reg_twoway2 <- plm(avg_initclaims_rate~home*cyber_sum+avg_case_rate+avg_death_rate, data= panel_use, model = "within", effect = "twoways")

summary(reg_twoway2)
```


$$ EmploymentRate_it = \beta_{1} StayAtHome_{it}*Cybersecurity_{i} + \beta_{2} CovidCase_{it}+  \beta_{3} CovidDeath_{it} + county_{i} + month_{t} $$
```{r}
reg_emp <- plm(emp_combined~home*high_cyber+avg_case_rate+avg_death_rate, data= panel_use, model = "within", effect = "twoways")


summary(reg_emp)

```

$$ LowIncomeEmploymentRate_it = \beta_{1} StayAtHome_{it}*Cybersecurity_{i} + \beta_{2} CovidCase_{it}+  \beta_{3} CovidDeath_{it} + county_{i} + month_{t} $$
```{r}
reg_emp_low <- plm(emp_combined_inclow~home*high_cyber+avg_case_rate+avg_death_rate, data= panel_use, model = "within", effect = "twoways")

summary(reg_emp_low)


```

$$ MidIncomeEmploymentRate_it = \beta_{1} StayAtHome_{it}*Cybersecurity_{i} + \beta_{2} CovidCase_{it}+  \beta_{3} CovidDeath_{it} + county_{i} + month_{t} $$
```{r}

reg_emp_mid <- plm(emp_combined_incmiddle~home*high_cyber+avg_case_rate+avg_death_rate, data= panel_use, model = "within", effect = "twoways")
summary(reg_emp_mid)

```

$$ HighIncomeEmploymentRate_it = \beta_{1} StayAtHome_{it}*Cybersecurity_{i} + \beta_{2} CovidCase_{it}+  \beta_{3} CovidDeath_{it} + county_{i} + month_{t} $$
```{r}

reg_emp_hight <- plm(emp_combined_inchigh~home*high_cyber+avg_case_rate+avg_death_rate, data= panel_use, model = "within", effect = "twoways")
summary(reg_emp_hight)
```


# Archived

## CPS data


```{r CPSarchive Prep, include=FALSE}
# State level
cps_data_demo<-cps_data # data backup
cps_data_demo$YearMonth <- with(cps_data_demo, sprintf("%d-%02d", YEAR, MONTH))

```


```{r Employment & geographcy related variables summary, eval=FALSE, include=FALSE, include=FALSE}

ipums_val_labels(cps_ddi, EMPSTAT)

ipums_val_labels(cps_ddi, LABFORCE)

ipums_val_labels(cps_ddi, OCC)#need to refer to documents 

ipums_val_labels(cps_ddi, IND)#need to refer to documents 

table(cps_data_demo$EMPSTAT)

# geo data summary

unique(cps_data_demo$STATEFIP)
unique(cps_data_demo$METAREA)
unique(cps_data_demo$COUNTY)
```

```{r Geography data clean - state, include=FALSE}

#cps-state
geo_code_state <- geo_code[c("state","stab")]
geo_code_state <- geo_code_state[!duplicated(geo_code_state$state),]
geo_code_state$state <- as.numeric(as.character(geo_code_state$state))

cps_data_demo$state_fip <- as.numeric(as.character(cps_data_demo$STATEFIP))
cps_data_demo <- merge(cps_data_demo, geo_code_state, by.x = "state_fip", by.y = "state", all.x = TRUE)
cps_data_demo <- merge(cps_data_demo,shelterdate[,c('abb','OrderMonth', 'OrderDay')], by.x = "stab", by.y = "abb", all.x = TRUE)



#ZIP-county data 
zip_county_use <- subset(zip_county, TOT_RATIO > 0.5 ) # Caveat

#MSA_County data
msa_county_use <- msa_county[,c(1,4,6)]
msa_county_use <- msa_county_use[!duplicated(msa_county_use),]

```


```{r Unemployment - CPS analyses, include=FALSE} 
#county level 

cps_data_demo %>% 
  filter( YearMonth > "2019-10") %>% 
  group_by(YearMonth,COUNTY) %>% 
  summarise(count = n(), 
         total_workforce = sum(EMPSTAT<30 & EMPSTAT!=0),
         unemployement = sum(EMPSTAT== 21 | EMPSTAT == 22),
         unemployment_rate = unemployement/total_workforce)

# Met area level  
cps_data_demo %>% 
  filter( YearMonth > "2019-10") %>% 
  group_by(YearMonth,METAREA) %>% 
  summarise(count = n(), 
         total_workforce = sum(EMPSTAT<30 & EMPSTAT!=0),
         unemployement = sum(EMPSTAT== 21 | EMPSTAT == 22),
         unemployment_rate = unemployement/total_workforce)
# State level

cps_data_demo %>% 
  filter( YearMonth > "2019-10") %>% 
  group_by(YearMonth,STATEFIP) %>% 
  summarise(count = n(), 
         total_workforce = sum(EMPSTAT<30 & EMPSTAT!=0),
         unemployement = sum(EMPSTAT== 21 | EMPSTAT == 22),
         unemployment_rate = unemployement/total_workforce)


cps_data_demo %>% 
  select(YearMonth,EMPSTAT,stab,OrderMonth) %>% 
  filter( YearMonth > "2019-10") %>% 
  count(YearMonth,EMPSTAT,stab,OrderMonth) %>% 
  group_by(YearMonth,stab) %>% 
  mutate(total = sum(n), 
         total_workforce = sum(n[EMPSTAT<30 & EMPSTAT!=0]),
         unemployement = sum(n[EMPSTAT== 21 | EMPSTAT == 22]),
         unemployment_rate = unemployement/total_workforce,
         stayathome = ifelse(is.na(OrderMonth), 0,1)) 

demo1 <- cps_data_demo %>% 
  select(YearMonth,EMPSTAT,stab,OrderMonth) %>% 
  filter( YearMonth > "2019-10") %>% 
  count(YearMonth,EMPSTAT,stab,OrderMonth) %>% 
  group_by(YearMonth,stab) %>% 
  mutate(total = sum(n), 
         total_workforce = sum(n[EMPSTAT<30 & EMPSTAT!=0]),
         unemployement = sum(n[EMPSTAT== 21 | EMPSTAT == 22]),
         unemployment_rate = unemployement/total_workforce,
         stayathome = ifelse(is.na(OrderMonth), 0,1))


```
## Descriptive analysis


```{r CI - mean & median, include=FALSE}

# State: Order by Cybersecurity investment
ci_data_use %>% select(SITEID, STATE, ZIPCODE.x, COUNTY,CBSA.Name, EMPLE, REVEN, cyber_sum,PCS, IT_BUDGET, HARDWARE_BUDGET,SOFTWARE_BUDGET,SERVICES_BUDGET) %>% 
  group_by(STATE) %>% 
  summarise_at(c("EMPLE","REVEN", "cyber_sum", "PCS", "IT_BUDGET", "HARDWARE_BUDGET", "SOFTWARE_BUDGET" , "SERVICES_BUDGET"), median, na.rm = TRUE) %>% 
  arrange(desc(cyber_sum))

# State: Order by Software budget
ci_data_use %>% select(SITEID, STATE, ZIPCODE.x, COUNTY,CBSA.Name, EMPLE, REVEN, cyber_sum,PCS, IT_BUDGET, HARDWARE_BUDGET,   SOFTWARE_BUDGET,SERVICES_BUDGET) %>% 
  group_by(STATE) %>% 
  summarise_at(c("EMPLE","REVEN", "cyber_sum", "PCS", "IT_BUDGET", "HARDWARE_BUDGET", "SOFTWARE_BUDGET" , "SERVICES_BUDGET"), mean, na.rm = TRUE) %>% 
  arrange(desc(SOFTWARE_BUDGET))


# County: Order by Cybersecurity investment
ci_data_use %>% select(SITEID, STATE, ZIPCODE.x, COUNTY,CBSA.Name, EMPLE, REVEN, cyber_sum,PCS, IT_BUDGET, HARDWARE_BUDGET,SOFTWARE_BUDGET,SERVICES_BUDGET) %>% 
  group_by(COUNTY) %>% 
  summarise_at(c("EMPLE","REVEN", "cyber_sum", "PCS", "IT_BUDGET", "HARDWARE_BUDGET", "SOFTWARE_BUDGET" , "SERVICES_BUDGET"), median, na.rm = TRUE) %>% 
  arrange(desc(cyber_sum))

# County: Order by Software budget
ci_data_use %>% select(SITEID, STATE, ZIPCODE.x, COUNTY,CBSA.Name, EMPLE, REVEN, cyber_sum,PCS, IT_BUDGET, HARDWARE_BUDGET,   SOFTWARE_BUDGET,SERVICES_BUDGET) %>% 
  group_by(COUNTY) %>% 
  summarise_at(c("EMPLE","REVEN", "cyber_sum", "PCS", "IT_BUDGET", "HARDWARE_BUDGET", "SOFTWARE_BUDGET" , "SERVICES_BUDGET"), mean, na.rm = TRUE) %>% 
  arrange(desc(SOFTWARE_BUDGET))

```

## Data visualization

```{r eval=FALSE, include=FALSE}
obs1 <- cps_data_demo %>% 
   count(YearMonth, EMPSTAT)

obs1 <- obs1 %>% 
  group_by(YearMonth) %>% 
  mutate(total = sum(n))

unemploy_exp <- obs1 %>% 
  filter(EMPSTAT == 21)

unemploy_new <- obs1 %>% 
  filter(EMPSTAT == 22)
unemploy_exp$prop <- unemploy_exp$n/unemploy_exp$total
unemploy_new$prop <- unemploy_new$n/unemploy_new$total

ggplot(unemploy_exp, aes(x = YearMonth, y =prop, group  = 1)) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title = "Experienced workers - Unemployment Rate", x = "Year-Month", y = "Proportion")

ggplot(unemploy_new, aes(x = YearMonth, y =prop, group  = 1)) +
  geom_line() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title = "New workers - Unemployment Rate", x = "Year-Month", y = "Proportion")

```


```{r unemployment, eval=FALSE, include=FALSE}

demo1 %>% 
  filter( stab %in% c("AL", "CA", "PA","NY","AK","SC","CT","AL", "NJ")) %>% 
  ggplot(mapping = aes(x = YearMonth, y = unemployment_rate, group  = 1)) +
  geom_line() + 
  facet_wrap(~stab, nrow =2)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept = "2020-04", colour="red") +
  ggtitle("Unmployment rate (States imposed stay-at-home order) ") + 
  ylab("Unemployment/Labor force")+
  theme(plot.title = element_text(hjust = 0.5))

demo1 %>% 
  filter(stayathome==0 ) %>% 
  ggplot(mapping = aes(x = YearMonth, y = unemployment_rate, group  = 1)) +
  geom_line() + 
  facet_wrap(~stab, nrow =2)+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  geom_vline(xintercept = "2020-04", colour="red") +
  ggtitle("Unmployment rate (No stay-at-home order )") + 
  ylab("Unemployment/Labor force")+
   aes(fill = as.factor(stayathome))+
   theme(plot.title = element_text(hjust = 0.5))


```
```{r}

demo1 %>% 
  group_by(YearMonth,stayathome) %>% 
  summarise(avg_unemployment = mean(unemployment_rate)) %>% 
  ggplot(aes(y = avg_unemployment,x = YearMonth, group = as.factor(stayathome), colour = as.factor(stayathome))) + 
  geom_line() +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  labs(title = "Unmployment rate (Average)", x = "Year-Month", y = "Unemployment/Labor force", color = "Stay-at-home-order") +
  scale_color_hue(labels = c("No", "YES")) +
  geom_line(size=2)


```


```{r shelter in place order}

shelterdate %>% 
  arrange(Order.Date) %>% 
  mutate(abb=factor(abb, levels = abb)) %>%
  ggplot(aes(x=abb, y= Order.Date)) + 
    geom_point() +
     theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


```


# QWI data

```{r Read QWI data}

# read each csv - for loop
qwifiles <- list.files(path = "data/QWI-DATA")
f <- list()
col <- c("geo_level", "geography", "industry","ownercode", "sex", "agegrp", "education", "firmage", "firmsize", "year", "quarter", "Emp", "EmpS",
"EmpTotal", "HirA", "FrmJbGn", "FrmJbLs", "FrmJbC", "EarnS", "Payroll")

for (i in 1:length(qwifiles)) {
  f[[i]] <- fread(paste("data/QWI-DATA/", qwifiles[i], sep = ""), select = col)
}

allqwidata <- rbindlist(f)

```

```{r Clean, reshape, and aggregate}
# extract state level and county level IT employment at 2019 Q4

## industry code
its_industry = c(5112, 5191, 5182, 5415)
computer_industry = c(3341, 3342, 3344, 3345, 5179)



# state_level
state_qwi_emp <- allqwidata  %>% 
  filter(geo_level=="S" ) %>% 
  select ( geography, year, quarter, industry, sex, education, Emp, EmpS,EmpTotal, EarnS, Payroll) 
  
## Reshape
state_qwi_emp_wide <- dcast(setDT(state_qwi_emp), geography+year+quarter+industry ~ paste0("sex", sex) + paste("education", education), value.var = c("EmpS", "EmpTotal","EarnS"), na.rm = TRUE, sep = "", sum)

colnames(state_qwi_emp_wide)  <- gsub(" ","",colnames(state_qwi_emp_wide))

state_qwi_agg <- state_qwi_emp_wide %>% 
  filter(year == 2019) %>% 
  group_by(geography, year,quarter) %>% 
  select(geography, year,quarter, industry, contains("E0")) %>%
    summarise(
              # EMPS
              its_emps_all = sum(EmpSsex0educationE0[industry %in% its_industry], na.rm=T),
              its_emps_male = sum(EmpSsex1educationE0[industry %in% its_industry], na.rm=T),
              its_emps_female = sum(EmpSsex2educationE0[industry %in% its_industry], na.rm=T),
              
              com_emps_all = sum(EmpSsex0educationE0[industry %in% computer_industry],na.rm=T),
              com_emps_male = sum(EmpSsex1educationE0[industry %in% its_industry], na.rm=T),
              com_emps_female = sum(EmpSsex2educationE0[industry %in% its_industry], na.rm=T),
              
                        
              all_emps_all = sum(EmpSsex0educationE0,na.rm=T),
              all_emps_male = sum(EmpSsex1educationE0, na.rm=T),
              all_emps_female = sum(EmpSsex2educationE0, na.rm=T),
              
              # EmpTotal
              
              its_empstotal_all = sum(EmpTotalsex0educationE0[industry %in% its_industry], na.rm=T),
              its_empstotal_male = sum(EmpTotalsex1educationE0[industry %in% its_industry], na.rm=T),
              its_empstotal_female = sum(EmpTotalsex2educationE0[industry %in% its_industry], na.rm=T),
              
              com_empstotal_all = sum(EmpTotalsex0educationE0[industry %in% computer_industry],na.rm=T),
              com_empstotal_male = sum(EmpTotalsex1educationE0[industry %in% computer_industry], na.rm=T),
              com_empstotal_female = sum(EmpTotalsex2educationE0[industry %in% computer_industry], na.rm=T),
              
              all_empstotal_all = sum(EmpTotalsex0educationE0,na.rm=T),
              all_empstotal_male = sum(EmpTotalsex1educationE0, na.rm=T),
              all_empstotal_female = sum(EmpTotalsex2educationE0, na.rm=T),
              
              # Earn
              
              its_earn_all = sum(EarnSsex0educationE0[industry %in% its_industry], na.rm=T),
              its_earn_male = sum(EarnSsex1educationE0[industry %in% its_industry], na.rm=T),
              its_earn_female = sum(EarnSsex2educationE0[industry %in% its_industry], na.rm=T),
              
              com_earn_all = sum(EarnSsex0educationE0[industry %in% computer_industry],na.rm=T),
              com_earn_male = sum(EarnSsex1educationE0[industry %in% computer_industry], na.rm=T),
              com_earn_female = sum(EarnSsex2educationE0[industry %in% computer_industry], na.rm=T),
              
              all_earn_all = sum(EarnSsex0educationE0,na.rm=T),
              all_earn_male = sum(EarnSsex1educationE0, na.rm=T),
              all_earn_female = sum(EarnSsex2educationE0, na.rm=T),
            
              ) %>% 
  ungroup()



#County level 

county_qwi_emp <- allqwidata  %>% 
  filter(geo_level=="C" ) %>% 
  select ( geography, year,quarter, industry, sex, education, EmpS, EmpTotal, EarnS, Payroll)
## Reshape
county_qwi_emp_wide<- dcast(setDT(county_qwi_emp), geography+year+quarter+industry ~ paste0("sex", sex) + paste("education", education), value.var = c("EmpS", "EmpTotal", "EarnS"), na.rm = TRUE, sep = "", sum)

colnames(county_qwi_emp_wide)  <- gsub(" ","",colnames(county_qwi_emp_wide))

county_qwi_agg <- county_qwi_emp_wide %>% 
  filter(year == 2019) %>% 
  group_by(geography, year,quarter) %>% 
  select(geography, year,quarter, industry, contains("E0")) %>%
    summarise(
              # EMPS
              its_emps_all = sum(EmpSsex0educationE0[industry %in% its_industry], na.rm=T),
              its_emps_male = sum(EmpSsex1educationE0[industry %in% its_industry], na.rm=T),
              its_emps_female = sum(EmpSsex2educationE0[industry %in% its_industry], na.rm=T),
              
              com_emps_all = sum(EmpSsex0educationE0[industry %in% computer_industry],na.rm=T),
              com_emps_male = sum(EmpSsex1educationE0[industry %in% its_industry], na.rm=T),
              com_emps_female = sum(EmpSsex2educationE0[industry %in% its_industry], na.rm=T),
              
                        
              all_emps_all = sum(EmpSsex0educationE0,na.rm=T),
              all_emps_male = sum(EmpSsex1educationE0, na.rm=T),
              all_emps_female = sum(EmpSsex2educationE0, na.rm=T),
              
              # EmpTotal
              
              its_empstotal_all = sum(EmpTotalsex0educationE0[industry %in% its_industry], na.rm=T),
              its_empstotal_male = sum(EmpTotalsex1educationE0[industry %in% its_industry], na.rm=T),
              its_empstotal_female = sum(EmpTotalsex2educationE0[industry %in% its_industry], na.rm=T),
              
              com_empstotal_all = sum(EmpTotalsex0educationE0[industry %in% computer_industry],na.rm=T),
              com_empstotal_male = sum(EmpTotalsex1educationE0[industry %in% computer_industry], na.rm=T),
              com_empstotal_female = sum(EmpTotalsex2educationE0[industry %in% computer_industry], na.rm=T),
              
              all_empstotal_all = sum(EmpTotalsex0educationE0,na.rm=T),
              all_empstotal_male = sum(EmpTotalsex1educationE0, na.rm=T),
              all_empstotal_female = sum(EmpTotalsex2educationE0, na.rm=T),
              
              # Earn
              
              its_earn_all = sum(EarnSsex0educationE0[industry %in% its_industry], na.rm=T),
              its_earn_male = sum(EarnSsex1educationE0[industry %in% its_industry], na.rm=T),
              its_earn_female = sum(EarnSsex2educationE0[industry %in% its_industry], na.rm=T),
              
              com_earn_all = sum(EarnSsex0educationE0[industry %in% computer_industry],na.rm=T),
              com_earn_male = sum(EarnSsex1educationE0[industry %in% computer_industry], na.rm=T),
              com_earn_female = sum(EarnSsex2educationE0[industry %in% computer_industry], na.rm=T),
              
              all_earn_all = sum(EarnSsex0educationE0,na.rm=T),
              all_earn_male = sum(EarnSsex1educationE0, na.rm=T),
              all_earn_female = sum(EarnSsex2educationE0, na.rm=T),
            
              ) %>% 
  ungroup()
             



```

```{r Descriptive analysis}
state_qwi_agg



```

