---
title: "Plots"
author: "Leting Zhang"
date: "8/28/2021"
update: "11/28/2021"
output: html_document
---

```{r Load library}

library(tidyverse)
library(here)
library(data.table)
library(haven)

```

# Config
```{r Path}
raw_data <- here("1.Data", "1.raw_data")
output <- here("1.Data", "3.output_data")
```


# Import the panel data
```{r import data}
# data

county_week <- read_dta(here("Stata", "county_week_panel_aug_analysis.dta"))
county_week <- as.data.frame(county_week)

```


```{r differentiate sample vs population}

mainvar <- c("county", "week", "month", "state", "initclaims_rate_regular", "emp_combined", 
             "avg_new_case_count", "avg_new_death_rate", "avg_home_prop", "it_budget_median", 
             "its_emps_all")

county_week_use <- county_week %>% 
  select(mainvar) %>% 
  filter(!is.na(initclaims_rate_regular) & !is.na(it_budget_median)) 

```

# Plots - Unemployment rate - Figure 1A

```{r Unemployment rate }
#saveRDS(ui_state_policy, here(output, "us_state_policy.rds" ))

us_state_policy <- readRDS("~/2.Covid_IT_Employment/1.Data/3.output_data/us_state_policy.rds")
 
# ui_state_policy
ggplot(data = ui_state_policy ,
            mapping = aes(x = month, y = initclaims_rate_regular,
                          group = state, color = factor(stayathome)) ) +
      geom_line() +
      geom_smooth(mapping = aes(group = stayathome), size= 1.5, se = TRUE) +
      coord_cartesian(c(min(ui_state_policy$month), max(ui_state_policy$month))) +  scale_x_continuous(breaks = seq(1,10,1), labels = function(x)month.abb[x])+
   scale_color_manual(name = "Stay at Home Order Enforcement", labels = c("No", "YES"),values=c( "#264653", "#e76f51"))+
      labs(x = "", y = " % Rate", title = "State Unemployment Insurance (UI) Claim Rate - 2020") +  
      theme_minimal() + 
      theme(plot.title = element_text(size = rel(1.6), hjust = 0.5),
           legend.title = element_text(size = rel(0.8)),
           plot.caption = element_text(size = rel(1)),
           legend.position = "top") +
    labs(caption = "Note: UI claim rates =  Number of initial claims per 100 people in the 2019 labor force.")
```


# Plots - Compare three unemployementa data sources - Figure 1B

```{r Compile data- Comparison between three data sources}
# Basic idea:  Extract covered county number
county_week <- read_dta(here("Stata", "county_week_panel_aug_analysis.dta")) # UI, Employment data
load("~/2.Covid_IT_Employment/CPS_2021.RData") # CPS data 


# Benchmark: All county 
mavar <-  c("county", "internetper", "medianhouseholdincome", "population", "totalhousehold")

county_char <-  county_week %>% 
  select(all_of(mavar)) %>% distinct()


# Unemployment insurance claim  - county

ui_county <- county_week %>% 
    select(county,initclaims_rate_regular ) %>% 
    filter(!is.na(initclaims_rate_regular)) %>% 
    mutate(ui = 1) %>% 
   select(county, ui) %>% distinct()

# Employment data - county

employ_county <- county_week %>% 
    select(county,emp_combined ) %>% 
    filter(!is.na(emp_combined)) %>% 
    mutate(payroll = 1) %>% 
    select(county, payroll) %>% distinct()

# CPS data  - county

cps_county <- cps_data %>% 
    filter(COUNTY!= 0 & YEAR == 2020) %>% 
    select(COUNTY) %>%
    distinct() %>% 
    mutate(cps = 1)

colnames(cps_county)[1] <- "county"


# Combine all data

county_datasource_all <- county_char %>% 
    left_join(employ_county) %>% 
    left_join(ui_county) %>% 
    left_join(cps_county)




#county_outcome_summary <- county_demo %>% left_join(need) # County population - merge with Chetty employment data
# need <- cps_use %>% 
#   mutate(cps = 1) %>% 
#   select(COUNTY, cps) %>% 
#   distinct() 
# 
# county_outcome_summary <- county_outcome_summary %>% left_join(need, c("countyfips" = "COUNTY"))
# 
# 
# need <- ui_county %>% 
#   mutate(ui = 1) %>% 
#   select(countyfips, ui) %>% 
#   distinct()
# 
# county_outcome_summary <- county_outcome_summary %>% left_join(need)


```


```{r Calculate the average}

data_obs_count <- county_datasource_all %>% 
  summarise(pop = n(),
            pay = sum(payroll == 1, na.rm = TRUE),
            cps = sum(cps == 1, na.rm = TRUE), 
            ui = sum(ui == 1, na.rm = TRUE)
            ) %>% gather(indicator, value, pop:ui) %>% 
  mutate(describe = "count") 


data_char_avg <- county_datasource_all %>% 
  summarise_at(c(2:5), mean, na.rm = TRUE ) %>% 
   mutate(indicator = "pop") %>% 
  add_row( # add payroll county 
    county_datasource_all %>% 
  filter(payroll == 1) %>% 
  summarise_at(2:5, mean, na.rm = TRUE ) %>% 
  mutate(indicator = "pay")
  ) %>% 
  add_row( # add ui county 
     county_datasource_all %>% 
  filter(ui == 1) %>% 
  summarise_at(2:5, mean, na.rm = TRUE ) %>% 
  mutate(indicator = "ui")
  ) %>% 
  add_row( # add cps county 
      county_datasource_all %>% 
  filter(cps == 1) %>% 
  summarise_at(2:5, mean, na.rm = TRUE ) %>% 
  mutate(indicator = "cps")
  ) %>% 
  gather(describe, value, 1:4, -indicator)



data_summary <-  data_obs_count %>% 
           add_row(data_char_avg)

# d3 <- county_outcome_summary %>% 
#   filter(cps == 1) %>% 
#   summarise_at(2:5, mean, na.rm = TRUE )%>% 
#   gather(desc, value, totalhousehold:medianhouseholdincome )%>% 
#   mutate(indicator = "cps")
# 
# d4 <- county_outcome_summary %>% 
#   filter(ui == 1) %>% 
#   summarise_at(2:5, mean, na.rm = TRUE )%>% 
#   gather(desc, value, totalhousehold:medianhouseholdincome )%>% 
#   mutate(indicator = "ui")
# 
# summary_outcome <- rbind(outcome_summary_use, d1, d2, d3, d4) 





data_summary <- data_summary %>% 
                mutate(value_use = value, 
                       value_use = ifelse(describe %in% c("population", "totalhousehold") , value/1000, value),
                       facet = recode(describe, "count" = "Total Observations",
                                      "internetper" = "Internet Percentage", 
                                      "medianhouseholdincome" = "Median Household Income", 
                                      "population" = "Population/1000", 
                                      "totalhousehold" = "Total Household/1000") )

data_summary$indicator <- factor(data_summary$indicator, level = c("pop", "pay", "cps", "ui" ))

data_summary$indicator <- factor(data_summary$indicator, level = c("cps", "pay", "ui", "pop" ))

data_summary <- data_summary %>% 
  mutate(benchmark = ifelse(indicator == "pop", "Benchmark", "Other Data Sources"))
```

```{r Plot}


library(ggpattern)

data_summary %>%  ggplot( aes(y = indicator , x = value_use)) +
                  geom_bar_pattern(aes(pattern = benchmark ), width = 0.4, stat="identity", fill = "gray")  +
                  scale_y_discrete(labels = c("pop" = "All Counties",
                                              "ui" = "Unemployment Insurance", 
                                              "pay" = "Payroll", 
                                              "cps" = "Current Population Survey"))+
                  scale_pattern_manual(values = c(Benchmark = "stripe", `Other Data Sources` = "none"))+ 
                  scale_alpha_manual(values = c(0.6,1)) +
                  facet_wrap(~facet, scales = "free_x") + 
                  theme_minimal()+  
                  labs(x = "", y = "", title = "Unemployement Data Sources: County-level Characteristics" ) +
                  theme(legend.position = "top", 
                        axis.title.y = element_blank(),
                        plot.title = element_text(size = rel(1.3), hjust = 0.5)) +
                  guides(pattern =guide_legend(title=""))

#scale_fill_manual(values = c("red","red","red","red")) +

```




# Plots - Unemployement rate - 2019 longer trend

```{r}

library(zoo)
# Read data: Unemployment rate 2019 2020
county_unemprate_19_20 <- readRDS("~/2.Covid_IT_Employment/1.Data/3.output_data/county_unemprate_19_20.rds")

# Process county name
county_unemprate_19_20 <- county_unemprate_19_20 %>% 
                          mutate(county_name = str_replace(county," County", ""), # Remove "County"
                                 county_name = substr(county_name, 1, nchar(county_name) - 3), #"Remove (U)"
                                 county_name = trimws(county_name)) %>%  #Remove leading/trailing white spaces
                          select(-c(series_id, county))


# Read data: county IT budget
county_week <- as.data.frame(read_dta(here("Stata", "county_week_panel_new.dta"))) 

county_it <- county_week %>% select(county, q4_high_it_budget_median) %>% distinct()

county_info <- read.csv(here(raw_data, "GeoIDs - County.csv"))
county_info <- county_info %>% 
  mutate(county_name = paste(countyname, ",", " ", stateabbrev, sep = "")) %>% 
  select(countyfips, county_name)

county_use <- county_it %>% 
  left_join(county_info, by = c("county" = "countyfips")) %>% 
  left_join(county_unemprate_19_20) %>% 
  filter(period != "M13") %>% 
  mutate(month = as.numeric(substr(period, 2, 3)),
         date = as.yearmon(paste(year,month, sep = "-")) )

```
```{r Summarize and calculate the mean value}
it_group_county_unemployrate <- county_use %>% 
  mutate(value = as.numeric(value)) %>% 
  group_by(q4_high_it_budget_median, date) %>% 
  summarise(unemployment = mean(value, na.rm = TRUE)) %>% 
  ungroup()
```

```{r Plot}

it_group_county_unemployrate %>% 
  
  ggplot(aes(x = date, y = unemployment, 
            color = factor(q4_high_it_budget_median) )) +
  geom_line(size= 1.2) +
  scale_color_manual(name = "High BAIT", labels = c("No", "YES"),values=c( "#264653", "#e76f51"))+
  labs(x = "", y = " % Rate", title = "County Unemployment Rate: 2019 - 2020") +  
      theme_minimal() + 
      theme(plot.title = element_text(size = rel(1.6), hjust = 0.5),
           legend.title = element_text(size = rel(0.8)),
           plot.caption = element_text(size = rel(1)),
           legend.position = "top") +
    labs(caption = "Data Source: U.S. Bureau of Labor Statistics - Local Area Unemployment Statistics (LAUS)")
  

```



```{r}

```




# IT investment

```{r IT investment -4th quantile}

# Density with segments (4th quantile)

 county_it_unique<- county_week_use %>% 
  select(county, it_budget_median) %>% 
  distinct()


 q4 <-  quantile(county_it_unique$it_budget_median)[4]


county_week_use %>% 
  select(county, it_budget_median) %>% 
  distinct() %>% 
  ggplot(aes(x = it_budget_median)) +
  geom_density() + 
  geom_vline(xintercept = q4, linetype="dashed", color = "blue") +
  annotate('text', x = q4+25000, y = 0.00007, label = "> High BAIT", color = "blue", size = 5)+
 #  geom_vline(xintercept = 46603, linetype="dashed", color = "orange") +
  #annotate('text', x = 46603+50000, y = 0.00005, label = "Orange County: 46603 USD", color = "orange", size = 5)+
  labs(x = "County-level median of IT Budget per Establishment (USD)", y = " Density", title = "2019 County-level Business Acess to IT Resources - Density") +  
      theme_bw()
  


```




```{r}
library(robustHD)
winsorize

b <- county_qwi_agg %>% select(geography, its_emps_all) %>% 
  mutate(it = log(its_emps_all + 1),
        it2 = winsorize(it))

b %>%
  right_join(county_map, by = c("geography"  = "county") ) %>% 
  ggplot(mapping = aes(x = long, y = lat, 
                       fill = it2, group = group)) +
      geom_polygon(color = "gray90", size = 0.05) +
      coord_equal() + 
    scale_fill_gradient2(high = "blue", mid = "white", low= "red", 
                         midpoint = 4.5, 
                         limit = c(0,11) ,
                         breaks = c(0, 4.5, 7,10), 
                         labels = paste(c( '0', '100', '1,000', '>20,000'))) +
      labs(fill = "") + theme_map() + theme(legend.position = "right")+  
  labs(x = "", y = "", title = " Number of IT Service Employees \nCounty Level") +  
      theme(plot.title = element_text(size = rel(2.5), hjust = 0.5),
           plot.caption = element_text(size = rel(1.2), hjust = 0),
           #legend.title = element_text(size = rel(1.5)),
            legend.text = element_text(size=15),
           legend.position = c(0.98, 0.40)) + labs(caption = "Source: Quarterly Workforce Indicators 2019")

```



# Archive
```{r Map}

ci_summarise_all %>% select(COUNTY,IT_BUDGET_median ) %>%
  mutate(it = log(IT_BUDGET_median)) %>% 
  right_join(county_map, by = c("COUNTY"  = "county") ) %>% 
  ggplot(mapping = aes(x = long, y = lat, 
                       fill = it, group = group)) +
      geom_polygon(color = "gray90", size = 0.05) +
      coord_equal() + scale_fill_gradient(high = "blue", low= "gray", breaks = c(9,8.5,8), labels = paste("$", c('8,103', '4,915', '2,980')) ) + 
      labs(fill = "") + theme_map() + theme(legend.position = "right")+  
  labs(x = "", y = "", title = "  IT Budget per Employee \nCounty Level") +  
      theme(plot.title = element_text(size = rel(2.5), hjust = 0.5),
           plot.caption = element_text(size = rel(1.2), hjust = 0),
           #legend.title = element_text(size = rel(1.5)),
            legend.text = element_text(size=15),
           legend.position = c(0.98, 0.40)) + labs(caption = "Source: CiTDB 2019")
```
```


```{r}

a <- ci_summarise_per_emp %>% select(COUNTY,IT_BUDGET_per_emp_median) %>%
  mutate(it = log(IT_BUDGET_per_emp_median + 1),
         it2= winsorize(it))

a %>%
  right_join(county_map, by = c("COUNTY"  = "county") ) %>% 
  ggplot(mapping = aes(x = long, y = lat, 
                       fill = it, group = group)) +
      geom_polygon(color = "gray90", size = 0.05) +
      coord_equal() + 
    scale_fill_gradient2(high = "blue", mid = "white", low= "red", 
                        limits=c(8,8.6),
                         breaks = c(8.045, 8.3, 8.6), 
                         midpoint = 8.3,
                         labels = paste("$", c('<2,980', '4,023', '>5,431')),
                         guide = "colorbar") +
      labs(fill = "") + theme_map() + theme(legend.position = "right")+  
  labs(x = "", y = "", title = "  IT Budget per Employee \nCounty Level") +  
      theme(plot.title = element_text(size = rel(2.5), hjust = 0.5),
           plot.caption = element_text(size = rel(1.2), hjust = 0),
           #legend.title = element_text(size = rel(1.5)),
            legend.text = element_text(size=15),
           legend.position = c(0.98, 0.40)) + labs(caption = "Source: CiTDB 2019")


```


